---
output: github_document

---

# 1 | Introduction

Since healthcare in one of the principle issues to be targeted in the United States, it is no surpise that medical insurance is the center of attention. Medical insurance firms study the risk depedning on the attributions of their beneficiaries, or customers in order to predict charges for new beneficiaries. 
In this report, we will examine the efficiency of charges of new beneficiaries for a medical insurance firm using a **linear regression model** in order to best predict the upcoming charges paid by the particular insurance company for new beneficiaries given certain attributes. In addition, we will also evaluate the how the model may be utilized to reduce cost associated with the firm's *wellness incentives program*, a program aimed to adopt more health behaviors and lifestyle by preventing bad health and illnesses. 

# 2 | Data Description 

The dataset contains the information and charges paid by a particular medical insurance company over a fixed time for 1,110 primary beneficiaries (i.e. customer) who purchased an insurance policy with corresponding conditions, which includes potentially covering medical expenses for their children.

Each primary beneficiary contains the following 7 variables: 

Variable |  Description  | Type 
--------------|--------------|-------------------------------------------------------------------------------------------------------
**age** |  age of beneficiary (in years)  |  Continuous 
**sex** |  sex of beneficiary (male or female)   | Categorical 
**bmi** |  body mass index (body mass in kilograms divided by the square of body height in meters)  | Continuous 
**children** |  number of children also covered by the beneficiary’s insurance policy  | Continuous 
**smoker**  |  indicates whether or not the beneficiary is a regular smoker  | Ordinal
**region** |   region of the United States in which the beneficiary lives (Northeast, Southeast, Southwest, Northwest)  | Categorical
**charges** |  medical costs billed to the insurance company (in dollars)  | Continuous

In this analysis, we focus on predicting the charges for a new beneficiary; `charges` is set as a response variable while the remaining six are set as explanatory variables (also known as predictor variables). In other words we will aim to predict the amount of charges covered for that customer within the fixed time frame given a particular attribute of customer. Afterwards, we will aim to interpret the cost reduction associated with changes of explanatory variables that might potentially affect the health of beneficiaries. 

```{r, echo= FALSE, message = FALSE}
data <- read.csv("~/Desktop/school/stat151A/midterm/MedicalInsurance.csv")
age <- data$age
sex <- data$sex
bmi <- data$bmi
children <- data$children
smoker <- data$smoker
region <- data$region
charges <- data$charges

#EDA Plots
library(ggplot2)
library(reshape2)
library(ggpubr)
library(dplyr)
library(gridExtra)
```

# 3 | Explanatory Data Analysis

Before diving into linear modelling or regressions, we will look more closely into the dataset to get a better understanding on the relationships of variables by visualizing the distribution.

## 3.1 | Univariate Relationship

To start our analysis, we need to briefly explore and understand the given dataset before modeling. The Figure 1a is the distribution of our response variable, `charges` through a histogram. It can be clearly observed that the dataset is skewed-right. Most of the beneficiaries had the insurance company pay below 15,000 dollars within the fixed time frame with the mean at around 10,000 dollars. 


```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height= 3, results='hide'}

figure1 <- ggplot(data=data, aes(x=charges)) +
  geom_histogram(bins=20, color = "black") + 
  labs(title = "Distribution of Charges", caption = "Figure 1a: Distribution of Charges", x = "charges (in dollars)")

logcharges <- log(charges)
sum(is.na(logcharges)) #2 NAN values
which(is.na(logcharges)) #80 and 730 
c(charges[80], charges[730]) #-999 and -999; negative values

figure2 <- ggplot(data=data, aes(x= logcharges)) +
  geom_histogram(bins=20, color = "black") + 
  labs(title = "Log Transformation of Distribution of Charges", caption = "Figure 1b: Log Transformation of Distribution of Charges", x = "log(charges)")

grid.arrange(figure1, figure2, ncol=2)
```

Since linear models are assumed to be normally distributed, we will perform a *log* transformation on the variable `charges` to `logcharges` in order to transform the highly skewed variable into a rather normally ditribubted variable as shown in Figure 1b. Note that when we take in effect of the *log* transformation, it will remove the data points of `charges` with a zero (or below) value as it will create `NaN`s for two beneficiaries. Upon a closer look, the data points that generated `NaN`s are most likely to be an error rather than an actual observation because there cannot exist a negative charge (insurance company paying back beneficiaries). 

```{r, echo = FALSE, message = 'hide', fig.width=10, fig.height = 4, results = 'hide'}
age.box <- ggplot(data=data,aes(x=age)) + 
  geom_boxplot() +
  labs(title="Distribution of Age")

sex.box <- ggplot(data=data, aes(x=sex)) +
  geom_boxplot() +
  labs(title="Distribution of Sexes")

maxbmi_df <- data %>%
  filter(bmi >140)

bmi.box <- ggplot(data=data, aes(x=bmi)) +
  geom_boxplot() +  
  geom_point(data=maxbmi_df, aes(y = 0), color = 'red') + 
  labs(title="Distribution of BMIs")
  

child.box <- ggplot(data=data,aes(x=children)) +
  geom_boxplot() +
  labs(title="Distribution of Children")

region.box <- ggplot(data=data, aes(x=region)) +
  geom_boxplot() +
  labs(title="Distribution of Regions")

smoker.box <- ggplot(data=data, aes(x=smoker)) +
  geom_boxplot() +
  labs(title="Distribution of Smokers")

grid.arrange(age.box, child.box, bmi.box, sex.box, region.box, smoker.box, ncol = 3,
             bottom = text_grob("Figure 2: Univariate Distribution of Explanatory Variables"))
```

```{r, echo = FALSE, results='hide'}
max.bmi <- max(bmi) #143.02
which(bmi > 143) #974
data$logcharges <- logcharges
data <- na.omit(data)
data <- data[data$bmi !=max.bmi, ]
```

In addition, in Figure 2, we observe that there exist an extreme outlier (indicated in red) in the univariate distribution of `bmi`. Since the value of BMI cannot be as large as that of the outlier (since  BMI is generally between 18.5 to 30), it is safe to assume that this outlier is also an error rather than an legitimate observation; as such going forward this point will be removed from the dataset. 


## 3.2 | Bivariate Relationship

#### 3.2.a | Bivariate Relationship of Numerical Explanatory Variables 

As mentioned in the previous section, *Section 2: Data Description*, the numerical explanatory variables include both continuous and ordinal type, thus the following: `age`, `bmi`, and `logcharges`. 

```{r,echo= FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 3, out.width= "50%", out.extra='style="float:right; padding:1px"'}
#correlation
continuous <- c("age", "bmi")

correlation_matrix <- round(cor(data[c(continuous, 'logcharges')]), 2)
melt_correlation_matrix <- melt(correlation_matrix)
ggplot(data = melt_correlation_matrix, aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + geom_text(aes(label = value), color = "white", size = 4) + 
  labs (title = "Correlation Plot of Numerical Variables", caption = "Figure 3: Correlation Plot of Numerical Explanatory Variables")
```

Firstly, from Figure 3, it can be seen that there is no negative correlation within the the variables, since they are all positive values. 

Secondly, though only a moderate correlation, `age` demonstrates the strongest correlation with `logcharges` of 0.47; meanwhile, there does not seem to be a significant correlation with `bmi`. 

Additionally, the explanatory variables are not closely correlated with one another, thus there is no collinearity existent. Instead, it appears that `bmi` and `age` has the weakest correlation of 0.13. This mean that the age of the beneficiary barely affects the bmi of beneficiary and vice versa, which is a logical statement since `bmi` is more related to how healthy the beneficiary is regardless of `age`. 


#### 3.2.b | Bivariate Relationship of Categorical Explanatory Variables 

```{r,echo= FALSE, warning = FALSE, fig.height= 3, fig.width= 10}
par(mfrow = c(1,4))
#sex
sex.box <- boxplot(log(charges) ~ sex, data = data, main = "Charges by Sex")
#children
children.box <- boxplot(log(charges) ~ children, data = data, main = "Charges by Children")
#smoker
smoker.box <- boxplot(log(charges) ~ smoker, data = data, main = "Charges by Smoker")
#region
region.box <- boxplot(log(charges) ~ region, data = data, main = "Charges by Region")

mtext("Figure 4: Bivariate Relationship for Categorical Variable", side= 3, line = -22.5, outer = TRUE, cex = 0.6)
```

From Figure 4, `logcharges` on average are similar regardless of `sex`, though the charges of males seem to be at a slightly wider variety. Whether the beneficiary is a `smoker` seem to affect the `logcharges` of health insurance companies the most, with the highest correlation with `logcharges`. This makes sense intuitively because smokers are more likely to be exposed to health issues. The variable `region` also is moderately correlated with `logcharges`. Those beneficiaries residing in the east coast seem to charge more than those residing in the west coast. Beneficiaries from southeastern region seem to charge the insurance company the most. This could be for a number of factors: weather, lifestyle, culture, etc. One asssumption could be that the southeastern region has the most states that has not yet enforced smoking bans in workplaces, restaurants, and bars. 

It seems that the beneficiaries with no children covered by the beneficiary's insurance policy have the highest average value of `logcharges`. This value drops with a presence of one child. The average of `logcharges` continues to increase from `children` value 1 to 4. However, there seems to be generally less variation in charges with insurance policy that cover higher number of `children`. One assumption could be because the higher number of `children` the beneficiary inclues in the insurance policy, the more occations the beneficiary has to charge the insurance company, but with less variety of reasons; comon reasons include flu, toothaches, etc. There seems to be multiple factors that could affect `logcharges` Figure 4. 

## 3.3 | Interactions

Apart from the indicator whether a beneficiary is a smoker or not: `smoker`, which has a strong correlation with the `logcharges` medical insurance companies cover for the beneficiary within the given time frame, the rest of the explanatory variables with correlations (`region`, `age`, `children`, and `bmi`) indicates that there is neither a strong nor weak correlation with the response variable. In order to explore more deeply into the relationship of the explanatory variables to the response variable, we will examine if there exists any significant interaction between the continuous variables(`age` and `bmi`) and categorical variables (`sex`, `smoker`,`region`, and `children`). 

```{r, echo = F, message = F, warning=F, fig.height= 5, fig.width=15}

#sex interaction with age and bmi
sex.age <- ggplot(data[data$sex == "male" |
                     data$sex == "female", ], 
              aes(x = cut_interval(x = age, length = 10), 
                  y = logcharges, color = sex)) + 
  geom_boxplot() + 
  xlab("Age") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. Age Categorized by Sex", color = 'Sex') +
  theme(plot.title = element_text(size = 10))

sex.bmi <- ggplot(data, aes(x = bmi, y = logcharges, color = sex)) + 
  geom_point(shape = 8) + 
  xlab("BMI") + 
  ylab("logcharges") + 
  xlim(c(0,60)) + 
  labs(title = "logcharges vs. BMI Categorized by Sex", color = 'Sex') +
  theme(plot.title = element_text(size = 10))

sex.interaction <- annotate_figure(ggarrange(sex.age, sex.bmi, ncol = 2, nrow = 1), top = text_grob("Interaction of logcharges by Age and BMI Categorized by Sex"))



#smoker interaction with age and bmi 
smoker.age <- ggplot(data[data$smoker == "yes" |
                     data$smoker == "no", ], 
              aes(x = cut_interval(x = age, length = 10), 
                  y = logcharges, color = smoker)) + 
  geom_boxplot() + 
  xlab("Age") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. Age Categorized by Smoker", color = 'Smoker') +
  theme(plot.title = element_text(size = 10))

smoker.bmi <- ggplot(data, aes(x = bmi, y = logcharges, color = smoker)) + 
  geom_point(shape = 8) + 
  xlab("BMI") + 
  ylab("logcharges") + 
  xlim(c(0,60)) + 
  labs(title = "logcharges vs. BMI Categorized by Smoker", color = 'Smoker') +
  theme(plot.title = element_text(size = 10))

smoker.interaction <- annotate_figure(ggarrange(smoker.age, smoker.bmi, ncol = 2, nrow = 1),
                top = text_grob("Interaction of logcharges by Age and BMI Categorized by Smoker"))


#region interaction with age and bmi 
region.age <- ggplot(data[data$region == "northwest" |
                     data$region == "northeast" |
                     data$region == "southwest" |
                     data$region == "southeast", ],
              aes(x = cut_interval(x=age, length =10),
                  y = logcharges, color = region)) + 
  geom_boxplot() + 
  xlab("Age") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. Age Categorized by Region", color = 'Region') +
  theme(plot.title = element_text(size = 10))


region.bmi <- ggplot(data, aes(x = bmi, y = logcharges, color = region)) + 
  geom_point(shape = 8) + 
  xlab("BMI") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. BMI Categorized by Region", color = 'Region') + 
  theme(plot.title = element_text(size = 10))

region.interaction <- annotate_figure(ggarrange(region.age, region.bmi, ncol = 2, nrow = 1),
                top = text_grob("Interaction of logcharges by Age and BMI Categorized by Region"))


#children interaction with age and bmi 
data["children"] <- as.factor(data$children)

children.age <- ggplot(data[data$children == "0" |
                     data$children == "1" |
                     data$children == "2" |
                     data$children == "3" |
                     data$children == "4" |
                     data$children == "5", ],
              aes(x = cut_interval(x=age, length =10),
                  y = logcharges, color = children)) + 
  geom_boxplot() + 
  xlab("Age") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. Age Categorized by Children", color = 'Children') +
  theme(plot.title = element_text(size = 10))


children.bmi <- ggplot(data, aes(x = bmi, y = logcharges, color = children)) + 
  geom_point(shape = 8) + 
  xlab("BMI") + 
  ylab("logcharges") + 
  labs(title = "logcharges vs. BMI Categorized by Children", color = 'Children') + 
  theme(plot.title = element_text(size = 10))

children.interaction <- annotate_figure(ggarrange(children.age, children.bmi, ncol = 2, nrow = 1),
                top = text_grob("Interaction of logcharges by Age and BMI Categorized by Children"))


annotate_figure(ggarrange(sex.interaction, smoker.interaction, region.interaction, children.interaction, ncol = 2, nrow = 2),
                bottom = "Figure 5: Interaction of logcharges by Age and Bmi with Categorical Variables")
```


Figure 5 generally displays that there is no significant relationship shown through interaction except for interaction with `smoker`. The relationship between both `age` and `bmi` with `logcharges` seem to depend on `smoker` of the beneficiary. In the graphs above, we can see that there is almost a parallel relationship between the smokers and non-smokers and age of beneficiaries to the `logcharges`. There is around a $20,000 jump between those who smoke and do not smoke and despite whether the beneficiaries are smokers or not, the beneficiaries seem to visit the hospital more often (charge the insurance company more) if they are older, which makes sense. 

In addition, there is a somewhat recognizable pattern with the non-smokers while a jump could be seen on the `logharges` with `smokers`. This implies that in general, non-smokers with higher `bmi` would be exposed to higher diseases such as heart disease, high blood pressure, diabetes etc. than non-smokers with lower `bmi` (the most healthy group of people!), but it is nowhere close to a `smoker`. A `smoker` status with a `bmi` higher than 25 are to exponentially increase health dangers as it is a fatal combination that determines health (imagine a person with bad health habits AND smokes). It can be observed that the indication whether a `smoker` has more affect on `logcharges` when interacted with `bmi` of the beneficiary than the `age` of the beneficiary. 

From these observations, there are likely to be two interaction terms in ourlinear regression model to predict `logcharges` of future potential beneficiaries: 1) `age` and `smoker` and 2) `bmi`and `smoker`. 

# 4 | Modeling, Prediction, Inference

Proceeding from our exploratory data analysis, we will fit a linear model to best predict `logcharges` of future potential benficiaries based on other attributes in the dataset; to find the best fit coefficients that best predict the change in `logcharges` given a unit change in the explanatory variable. 

Here, we define the *null model* to be a intercept-only model that describes the response variable, `logcharges`. We also define the *full model* as follows, which includes all predictor variables still under consideration, in addition to interaction terms. The simple linear regression model follows the function in which *y* is the response variable `logcharges`, *X* is the design matrix of explanaotry variables, and ε is the error vector. 

*y = β₀ + Xᵢβᵢ + ε*

Our goal for this analysis is to best predict our response variable `logcharges` simulatenously means to find the model that "best fit" the dataset; following the ordinary least squares equation. This implies that the coefficients that best fit the dataset is to minimize of the error sums of squares. 

In order to build a linear regression model, firstly, the initial model (inclusion of each explanatory variable with no interactions) is set as below: 

![formula](https://render.githubusercontent.com/render/math?math=logcharges%20~%20age%2Bbmi%2Bchildren%2Bsex%2Bsmoker%2Bregion)

As the goal for the analysis is to *predict* the `logcharges` of new beneficiaries, a 80-20 split for a train-test will be performed. 885 observations will be used to construct the model of best fit while the remaining 222 observations will be used to assess the prediction performance of the constructed model. 

```{r, echo = FALSE, results= 'hide'}
set.seed(2020)
trainindex <- sample(c(rep(0, 0.8 * nrow(data)),
                       rep(1, 0.2* nrow(data))))

train <- data[trainindex == 1, ]
test <- data[trainindex == 0, ]
```

```{r, echo = FALSE, results = 'hide'}
init.model <- lm(formula = logcharges ~ age + bmi + children + sex + smoker + region,  data = train)

summary(init.model)
```

The initial model has a multiple R^2^ value of 0.7 and an adjusted R^2^ value of 0.7266, indicating fairly satisfactory initial model. The p-values are low with most of the coefficients being statistically significant with the corresponding p-value of below the 5% level (See *Appendix* for R output). However, the best model is not always the most complicated, thus the full model is not necessary in building the model because too many variables can bring up issue of collinearity; estimate might not be biased, but variance is affected. 

Before looking into interactions, the explanatory variables will be observed. Since the statistical significance of the explanatory variables `sex` and `children` were not definite from *Section 3.2.b | Bivariate Relationship of Categorical Explanatory Variables*, an incremental one-sided F-test will be proceeded by using the `anova` function to compare competing models with and without the presence of the repsective coefficients and the "null model" in order recognize areas of improvement from the initial model; the null model is when the respective coefficients are values of 0. 

```{r, echo = FALSE, results= 'hide'}
model.1 <- lm(logcharges ~ age + bmi + smoker + region, data = train) 
model.2 <- lm(logcharges ~ age + bmi + smoker + region + children, data = train) 
model.3 <- lm(logcharges ~ age + bmi + smoker + region + children + sex, data = train) 

anova(model.1, model.2, model.3)
```

Model | Forumla | Residual Degrees of Freedom  |  Residual Sums of Squares | Degrees of Freedom  | Sum of Squares  | F | Pr(>F)
------|---------|------------------------------|---------------------------|---------------------|-----------------|---|-----------
Null Model | logcharges ~ age + bmi + smoker + region | 214 | 45.141  |
Model with Children | logcharges ~ age + bmi + smoker + region + children | 209 | 41.530 | 5 | 3.6111 | 3.6877 | 0.003218 **
Model with Children + Sex | logcharges ~ age + bmi + smoker + region + children + sex | 208 | 40.736 | 1 | 0.7935 | 4.0518 | 0.045412 * 

From the Table above, though both models have a significant p-value below 0.05, the **Model with Children + Sex** barely passes with a value of 0.045; the explanatory variable `sex` will be excluded from the final model, while including `children`. 


Considering the interactions examined in *Section 3.3: Interactions*, the interactions of `smoker` and variables `age` and `bmi` will be considered. Similarly, the results of the incremental F-tests is computed below: 

```{r, echo = FALSE, results='hide'}
model.1 <- lm(logcharges ~ age + bmi + smoker + region + children, data = train) 
model.2 <- lm(logcharges ~ age + bmi + smoker + region + children + age:smoker, data = train) 
model.3 <- lm(logcharges ~ age + bmi + smoker + region + children + age:smoker + bmi:smoker, data = train) 

anova(model.1, model.2, model.3)
```

Model | Forumla | Residual Degrees of Freedom  |  Residual Sums of Squares | Degrees of Freedom  | Sum of Squares  | F | Pr(>F)
------|---------|------------------------------|---------------------------|---------------------|-----------------|---|-----------
Model | logcharges ~ age + bmi + smoker + region + children | 209 | 41.530  |
Model with Age:Smoker | logcharges ~ age + bmi + smoker + region + children + age:smoker | 208 | 34.724 | 1 | 6.8060 | 43.533 | 3.424e-10 ***
Model with Age:Smoker + BMI:Smoker | logcharges ~ age + bmi + smoker + region + children + age:smoker + bmi:smoker | 207 | 32.363 | 1 | 2.3612 | 15.103 | 0.000137 *** 

Both interactions are significant as the p-values are safely below 0.05, thus both interactions will be included in the model. Thus, the final linear regression model for this analysis has been completed with the following coefficients: `age`,`bmi`,`smoker`,`region`,`children`,`age:smoker`, and `bmi:smoker`.  

# 5 | Model Diagnostics

Our final model, with 14 regressor terms including the intercept, is as below: 

![formula](https://render.githubusercontent.com/render/math?math=logcharges%20~%20age%2Bbmi%2Bsmoker%2Bregion%2Bchildren%2Bage:smoker%2Bbmi:smoker)

```{r, echo=FALSE, results='hide'}
model <- model.3

summary(model)
```

The model has a Multiple R^2^ value of 0.7946, an Adjusted R^2^ value of 0.7817 and a low p-value, which is fairly satisfactory (See *Appendix* for R output). However, this model still raise areas of concerns. First and foremost, as we assumed `children` to be a categorical variable rather than a continous variable (as it was an ordinal type), inidicating an overfitting of the data. Additionally, the `smoker`, `children5`, and potentially `children4` coefficients have a fairly large standard error values of around 0.36, 0.29, and 0.17 respectively, indicating wide range of uncertainity on the prediction. Finally, with the addition of interactions, some coefficients such as `bmi`, `children3`, and `children5` are no longer below the p value of 0.05, thus not statistically significant. 

```{r, echo = FALSE, fig.width=10, fig.height=4}
residual <- data.frame(model$fitted.values, model$residuals)

residual.plot <- ggplot(data=residual, aes(x=model$fitted.values, y = model$residuals)) +
  geom_point(shape = 1) + 
  labs(x= "Fitted Values", y = "Residuals",
       title = "Residuals vs. Fitted Values",
       caption = "Figure 6a: Residual Plot vs. Fitted Values for Final Model") 

model.fittedvalues <- model$fitted.values
model.residuals <- model$residuals
mean.residual <- mean(residual$model.residuals)
sd.residual <- sd(residual$model.residuals)

residual$standardized.residuals <- ((residual$model.residuals - mean.residual) / sd.residual)
  
normal.qqplot <- ggplot(data = residual, aes(sample = standardized.residuals)) +
  stat_qq(shape = 1, fill = "black") + stat_qq_line(color = "blue") + 
  labs(x="Theoretical Quantiles", y="Standardized Residuals", 
       title="Normal Q-Q Plot", 
       caption="Figure 6b: Normal Q-Q Plot for Final Model")

grid.arrange(residual.plot, normal.qqplot, ncol = 2)
```

The final model derived implies a biased prediction for some data points and does not follow the linear regression normality assumptions for serveral reasons. Based on Figure 6, there is no linearity for our response variable as shown as the residual errors does not portray homoscedasticity. The response variable `logcharges` does not follow the linear regression normality assumptions because as illustrated in Figure 1b, the dataset only has a **roughly** normal distribution from our initial log tranformation. Another reason of non-normality is from the long right-tail displayed from the Normal Q-Q Plot of Figure 6b. Nevertheless, the model will proceed to be used for interpretation and prediction. 

# 6 | Model Interpretation

In order to proceed to prediction of our final linear regression model, there are a few keypoints to be mentioned. The model has an Adjusted R^2^ value of 0.7397, which indicates a good fit, capturing around 80% of the variance in `logcharges`. 
Let ŷ be the predicted `logcharges` of a beneficiary. In regards to the regressor coefficients, the coefficients of the final model is the partial relationship between y and its respective x after all the explanatory variables are "proejected out". For instance, one unit increase in `age` will lead to a change by 0.037416 in ŷ, holding all other coefficients constant. An one unit increase in `bmi` will lead to an average increase of ŷ by 0.003282, holding all other coefficients constant. 

In regards to the categorial variables, `children`, `smoker`, and `region` have been separated into unique dummy variable columns (also known as an indicator variable); all the categorical variables are binary for this analysis. The variables `smoker` (yes/no) is encoded as a single dummy variable column; a beneficiary who is a smoker would hold an increase of average log ŷ value of 1.315989 more than a beneficiary who does not smoke, holding all other coefficients constant. 
In addition, `children` and `region` have more than 2 "options". In this case, the model will drop one 'value' and define k-1 dummy variables; the model drops  "regionnortheast" and "children0". The dummy variables of the categorical variable will be defined as 0's and 1's (0 represents absence of the qualitative attribute and 1 represents the presence of the qualitative attribute). A beneficiary who has 1,2,3,4,5 children will increase of log ŷ value by an average of 0.174946, 0.198201, 0.148452, 0.732462, and 0.293686 repsectively. Similarly, if a beneficiary lives in the northwest, southeast, and southwest region of the United States, the log ŷ value will decrease by an average of 0.219354, 0.207655, and 0.267488 respectively. However, it is difficult to interpret the relative importance of categorical variables since there is one categorical group in the intercept and we cannot interpret the intercept term. It is worth mentioning that the intercept is not scientifically interesting because no beneficiaries have age 0. 

In regards to the interaction terms, `age:smoker` indicates that the linear relationship of `age` and `logcharges` or "slope of the coefficient" can vary depending on the `smoker` status of the beneficiary. Similarly, `bmi:smoker` indicates that the linear relationship of `bmi` and `logcharges` or "slope of the coefficient" can vary depending on the `smoker` status of the beneficiary. One intersting result from the model is that `age:smokeryes` has a negative coefficient, meaning that an older beneficiary who smokes supposedly has lower medical charges, which sounds counterintuitive. When interpreted with `age`,-0.031184 + 0.037416 = 0.006232, it will generate a positive coefficient. Again, as the interactions are of numerical and categorical variable, since we cannot standardize coefficients to compare the relative importance of variables, it will be difficult to interpret the interaction variables as well.  

# 7 | Prediction 

As the main goal of the analysis was to predict the `logcharges`through the model genereated from the train set, we will test the predictions onto the 222 observations set aside in order to test our model's performance on predicting charges of new potential beneficiaries. 

```{r, echo = FALSE, fig.width= 10, fig.height = 5}
test.prediction <- predict(model, newdata=test, interval="prediction", level=0.95) # test set predictions
train.prediction <- predict(model, newdata=train) # train set predictions
test.logcharges <- test$logcharges

fit.plot <- ggplot(data.frame(test.prediction), aes(x=test.logcharges, y=fit)) +
  geom_point() +
  geom_smooth(aes(color="model"), stat="smooth", method="gam", formula=y~s(x, bs="cs")) +
  geom_line(aes(x=seq(min(test.logcharges), max(test.logcharges), length.out=length(test.logcharges)),
                y=seq(min(test.logcharges), max(test.logcharges), length.out=length(test.logcharges)),
                color="ideal")) + labs(x="Actual", y="Predicted",
       caption="Figure 7: Linear Model Fit of Predicting Log Charges for Potential Beneficiaries") +
  scale_color_manual("linear relation", values=c("red", "blue")) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = c(0.25, 0.8)) + 
  ggtitle("Predicting Log Charges for Potential Beneficiaries") +
  annotate(geom="text", x=10, y=7.5, label=paste("Train RMSE =", 
                                                 round(sqrt(mean((train.prediction - train$logcharges)^2)), 2)), color="red") + 
  annotate(geom="text", x=10, y=7, label=paste("Test RMSE =",
                                               round(sqrt(mean((test.prediction - test$logcharges)^2)), 2)), color="red")

fit.plot
```

Figure 7 is a relative fit of our final model, visualizing the root mean square error (MSE) of the training and testing set; as shown above, the actual model (in blue) with 95% confidence interval (shaded along the blue line) does not fit with the ideal model (in red). In addition, the Root Mean Squared Error (RMSE) of the training and testing set is around 0.38 and 0.77 respectively, displaying a poor performance of prediction as the values are far apart from each other. 

# 8 | Casual Inference | Wellness Plan

As the analysis is to predict `logcharges`, we will limit ourselves to make association assumption from our model. Even though casual relationship may not hold, even when other regressors are held constant, it can still be important to note that `smoker` status can increase medical insurance charges. Although there might be other variables that needs to be taken into consideration or a different model for this dataset, it is intuitive that smoking can cause a higher chance of health problems. Alternatively, `smoker` is not a *direct* cause of health issue (and cause medical charges to increase), but can be an indirect cause that could trigger the possibility of cardiovascular or respiratory diseases. 

The particular insurance company is considering to start a wellness incentives program that encourages beneficiares to adapt more healthy behaviors. the goal is to reduce charges by preventing health and illness. This plan would intuitively control the `bmi` and `smoker` regressors as other regressors cannot be altered as directly. However, the model generated from this analysis is not an accurate model to assess the wellness incentives program for several reasons. 

As `smoker` status affects the charges of beneficiaries the most according to the model, in order to reduce medical charges, it would be the most sensible choice to stop smoking for the beneficiaries who smoke. However, this would only work to a certain extent and is not the ultimate solution as it depends on other factors of the beneficiary: how heavy of a smoker they were, how long they have been smoking for, if they are still exposed to second-hand smoking etc. 

Moreover, as `bmi` decreases, it can be initially predicted that the charges of the medical insurance would decrease as well as from the interaction regressor `bmi:smokeryes` indicates a positive coefficient. As mentioned in *Section 6: Model Interpretation*, as the `bmi:smokerno` is included in the intercept term, which cannot be closely evaluated or interpreted, it would be impossible to predict the effect of `bmi` even when a beneficiary stops smoking from this model. Even though we are not sure of the effects a beneficiary when he stops smoking, but we will be able to predict that the beneficiary will be able to lower insurance charges if the particular beneficiary continues smoking, but adapt a healther lifestyle and lose weight (lower `bmi` levels). 

Aside these reasons, since we have resulted that our linear model had a poor performance, the cost reduction prediction from altering behaviors of beneficiaries according to our model is not reliable.   

# 9 | Conclusion 

In this analysis, we have analyzed the dataset on charges of medical insurance on beneficiaries and were to predict charges of potential future beneficiaries given certain attributes and information. Although the final linear regression model derived from the report initially seemed perform accurately in predicting potential charges when tested on the testing data, it raised some concerns and limitations on the key aspect of normality assumption of linear regression method as well as underlying confounding factors that were not considered in the dataset. For these reasons, a linear regression model is not the best approach in modeling the data to predict charges of future beneficiaries. 



